---
title: "New Analysis"
description: |
  This page showcases one new data analysis and visualization I created using everything I learned in HIA229.
color1: "lightpink"
color2: "lavender"
angle: 130
output:
  postcards::onofre
---

The scatterplot below illustrates the relationship between global sales (in millions) and critic scores for various video games. Each point represents a video game, with the color indicating its genre, enhancing categorical differentiation. The plot includes jittering to minimize overplotting, making it easier to distinguish individual points.

Two reference lines, drawn at the mean critic score and mean global sales, serve as benchmarks. These lines, coupled with their respective annotations, provide a quick visual reference to understand how individual games perform relative to the average. The use of these statistical measures helps in identifying outliers and patterns within the data. This visualization not only demonstrates the dispersion and central tendency of the data but also highlights the genre-wise distribution and its impact on both sales and critical reception, offering a comprehensive overview of trends within the video game industry.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, warning = FALSE, message = FALSE}
library(ggplot2)
library(dplyr)

videogames <- read.csv("videogames.csv")

videogames_clean <- videogames %>%
  filter(!is.na(Critic_Score) & !is.na(Global_Sales) & !is.na(Genre) & !is.na(Publisher))

mean_critic_score <- mean(videogames_clean$Critic_Score, na.rm = TRUE)
mean_global_sales <- mean(videogames_clean$Global_Sales, na.rm = TRUE)

ggplot(videogames_clean, aes(x = Critic_Score, y = Global_Sales, color = Genre)) +
  geom_jitter(alpha = 0.4, shape = 18, size = 2) +  
  geom_vline(xintercept = mean_critic_score, linetype = "dotted", color = "black", size = 0.7) +  
  geom_hline(yintercept = mean_global_sales, linetype = "dotted", color = "black", size = 0.7) +  
  annotate("text", x = mean_critic_score, y = max(videogames_clean$Global_Sales, na.rm = TRUE), 
           label = "Mean Critic Score", vjust = -0.05, size = 3) + 
  annotate("text", x = max(videogames_clean$Critic_Score, na.rm = TRUE), y = mean_global_sales, 
           label = "Mean Global Sales", hjust = 0.8, size = 3) + 
  labs(
    title = "Critic Score vs. Global Sales by Genre",
    x = "Critic Score",
    y = "Global Sales (in millions)",
    color = "Genre"
  ) +
  theme_bw() + 
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),  
    axis.text.x = element_text(angle = 45, hjust = 1),  
    legend.position = "top"
  )
```




